\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-28 manuscript.Rnw
Remove comments from code chunks

states <- data.table(
  state_id = c(1, 2),
  state_name = c("Stable", "Progression") # Non-death health states
)

@@

<<ictstm_stvalmods>>=
# Utility
utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
                               hesim_data = hesim_dat)

# Costs
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
                                time_reset = TRUE, hesim_data = hesim_dat)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
                               hesim_data = hesim_dat)
costmods <- list(Drug = drugcostmod,
                 Medical = medcostmod)
@

@@

<<rr>>=
x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
            xbeta(x_rr, params_rr_rng$rr_13))
head(rr) # Corresponds to 1st 6 rows in tpmat_id
@

@@

<<cea>>=
wtp <- seq(0, 250000, 500) # Willingness to pay per QALY
cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
                        dr_qalys = .03, dr_costs = .03,
                        k = wtp)
@

>>>>

states <- data.table(
  state_id = c(1, 2),
  state_name = c("Stable", "Progression") 
)

@@

<<ictstm_stvalmods>>=
utilitymod <- create_StateVals(utility_tbl, n = n_samples, 
                               hesim_data = hesim_dat)
drugcostmod <- create_StateVals(drugcost_tbl, n = n_samples,
                                time_reset = TRUE, hesim_data = hesim_dat)
medcostmod <- create_StateVals(medcost_tbl, n = n_samples,
                               hesim_data = hesim_dat)
costmods <- list(Drug = drugcostmod,
                 Medical = medcostmod)
@

@@

<<rr>>=
x_rr <- as.matrix(transmod_data[, .(soc, new1, new2)])
rr <- cbind(xbeta(x_rr, params_rr_rng$rr_12),
            xbeta(x_rr, params_rr_rng$rr_13))
head(rr) 
@

@@

<<cea>>=
wtp <- seq(0, 250000, 500) 
cea_ictstm <- cea(ce_sim_ictstm, dr_costs = .03, dr_qalys = .03, k = wtp)
cea_pw_ictstm <- cea_pw(ce_sim_ictstm, comparator = 1,
                        dr_qalys = .03, dr_costs = .03,
                        k = wtp)
@
